---
title: "Intro to Plotly"
author: "Ian G. Brennan"
#date: "02/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

GIFs are great and all, but what about if we want to create *really* interactive plots?


Start by installing and loading the two packages. We'll be relying on *plotly*
```{r, message=F, warning=F}
library(plotly)
library(RColorBrewer)
```

```{r, include=F, eval=F}
setwd("~/Documents/GitHub/CommunicatingFigures")
```

One last time, we'll read in the same data we've been playing with already.  
I realize you probably all hate monitor lizards already. It's ok, we're almost done.
```{r}
goannas <- readRDS("Goannas.RDS")
traits <- mutate(goannas$size.data,
                 TailRatio = Tail/Body_Length)
```

*plotly* works in a different way from *ggplot* and *gganimate*, but the syntax is perhaps more intuitive.  
Let's get the plot then break it down.
```{r}
sizes <- plot_ly(traits, 
        x = ~Body_Length, 
        y = ~Tail, 
        text = ~paste("Species: ", Name_in_Tree,
                      "<br> Habitat: ", Habitat), 
        type = 'scatter', 
        mode = 'markers', 
        color = ~TailRatio, 
        colors = 'YlGnBu',
        marker = list(size = ~TailRatio*20, 
                      opacity = 0.75, 
                      sizemode = "diameter",
                      line = list(width = 2, 
                                  color = "black"))) %>%
  layout(title = 'Monitor Lizard Body and Tail Length',
         xaxis = list(type = "log"),
         yaxis = list(type = "log"))
```

```{r, echo=F}
sizes
```

Just like you expect, we've designated:

* x axis: Body_Length
* y axis: Tail (length)
* text: what we want displayed when we hover over a point
* type: scatter plot
* color: Tail/Body_Length ratio
* colors: this will take RColorBrewer palettes, nice!
* marker: specifics of our point aesthetics
* layout: give it a title, and the scale for the axes

\  

If you decide you want to save your plot online instead of generating it new each time, you could sign up for a *plotly* account. It only takes a minute, and the instructions can be found on the [*plotly* website](https://plot.ly/r/getting-started/).  

Once you're all signed up, you can save individual plots using the 'api_create' function, which will push them to your *plotly* account online.
```{r, eval=F}
api_create(sizes, filename = "Varanus_SVL_vs_Tail")
```
